Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-08 paper/main.tex
dropping comments

\todo[inline]{SE: Vergleich zu Faces aus? COH: should be clearer now why we did
not do it}

\todo[inline]{SE: cuts to new vs familar setting wird irgendwie nie so
richtig in den PPA kontext eingeordnet. Warum ist das Hauptkontrast und nicht
das viel näher liegende places vs faces? COH: places vs. face = simple set in
Sengupta; here, we follow the strict set used in Sengupta; tbh, not mentioned in
detail}

@@

\todo[inline]{SE: Wie sehen die Antworten innerhalb der "klassisch definierten"
PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber
places vs faces) aus? COH: ???}

@@

\todo[inline]{part regarding Sengupta is shortened; they used $t$-maps???}
% Sengupta et al., 2016
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registed to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

>>>>

\todo[inline]{COH: tried to make clear why we did not/could not use ``places vs.
faces''}

@@

\todo[inline]{SE: Antworten innerhalb "klassisch definierter"
PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber
places vs faces) aus? -> Peristimulus plots}

@@

% Sengupta et al., 2016
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).\todo{I shortened the following part (maybe too
much)}
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
\todo{they used $t$-maps???}
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registed to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.
